Natural Stories LM analysis

### 2020-07-23 Analysis/nat_stories_lms.Rmd
add attempt at loglik

---
title: "Natural Stories LM analysis"
output: github_document
---
```{r, include=F}
knitr::opts_chunk$set(echo = FALSE, warning=F)
options(knitr.table.format = "html")
library(tidyverse)
library(readr)
library(brms)
library(lme4)
library(rstan)
library(tidybayes)
library(knitr)
library(mgcv)
library(mgcViz)
library(tidymv)
theme_set(theme_bw())
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
```

@@

```{r}
summary(brm_ngram_interact_post)
summary(brm_ngram_interact)

summary(brm_grnn_interact_post)
summary(brm_grnn_interact)

summary(brm_txl_interact_post)
summary(brm_txl_interact)
```

@@

```{r}
# a <- log_lik(brm_ngram_interact)
# 
# a2 <- add_criterion(brm_ngram_interact, "waic")
# 
# b <- log_lik(brm_grnn_interact)
# 
# c <- log_lik(brm_txl_interact)
```

>>>>

---
title: "Natural Stories LM analysis"
output: github_document
---
```{r, include=F}
knitr::opts_chunk$set(echo = FALSE, warning=F)
options(knitr.table.format = "html")
library(tidyverse)
library(readr)
library(brms)
library(lme4)
library(rstan)
library(tidybayes)
library(knitr)
library(matrixStats)
theme_set(theme_bw())
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
```

@@

```{r}
# summary(brm_ngram_interact_post)
# summary(brm_ngram_interact)
# 
# summary(brm_grnn_interact_post)
# summary(brm_grnn_interact)
# 
# summary(brm_txl_interact_post)
# summary(brm_txl_interact)
```

@@

#given a vector of logs, find harmonic mean
#uses one of the formulae from wikipedia page so we have underflow and not overflow issues
#then use logSumExp to reduce underflow
get_harmonic <- function(d){
  l <- length(d)
  log_prod <- sum(d) #this is the log of the product 
  log_inv <- d*-1 # this is list of logs of inverses
  log_inv_prod <- log_inv+log_prod #we "multiply" by the product, all of these are now teeny
  log_sum <- logSumExp(log_inv_prod) #we sum these up, still logged
  overall <- l * exp(log_prod-log_sum)

  overall
}

 a <- log_lik(brm_ngram_interact)

 b <- log_lik(brm_grnn_interact)

 c <- log_lik(brm_txl_interact)

 get_harmonic(a)

 get_harmonic(b)

 get_harmonic(c)
```

I get 9.087e-32 for Ngram, 3.602e-32 for GRNN, and 2.24e-33 for TXL. I'm not sure this is the order we expect, and not sure how to interpret it. (Also not sure I did things right.)
